---
title: "Cointrum Model Testing"
author: "Jordan Emslie"
date: "26/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cointrum Model Testing


Get some candle Data from Cointrum API
```{r}
library("rjson")
json_file <- "http://localhost:3001/api/v1/phds/Binance/candles?basecurrency=BNB&altcurrency=BTC&interval=1m&start=1587657944046&end=1587687944046&,"
json_data <- fromJSON(paste(readLines(json_file), collapse=""))
```

Reformat Data to R standards
```{r}

# R Dataframe values
openTime <- c()
open<- c()
high<- c()
low<- c()
close<- c()
volume<- c()
closeTime<- c()
quoteVolume<- c()
trades<- c()
baseAssetVolume<- c()
quoteAssetVolume<- c()

# Creata a sense of Amount increase for a Response Variable
value <- 100
amount <- c()

for(ChartTuple in json_data){
  openTime <- c(openTime, ChartTuple[2]$openTime)
  open <- c(open, ChartTuple[3]$open)
  high <- c(high, ChartTuple[4]$high)
  low <- c(low, ChartTuple[5]$low)
  close <- c(close, ChartTuple[6]$close)
  volume <- c(volume, ChartTuple[7]$volume)
  closeTime <- c(closeTime, ChartTuple[8]$closeTime)
  quoteVolume<- c(quoteVolume, as.numeric(ChartTuple[9]$quoteVolume))
  trades<- c(trades, ChartTuple[10]$trades)
  baseAssetVolume<- c(baseAssetVolume, ChartTuple[11]$baseAssetVolume)
  quoteAssetVolume<- c(quoteAssetVolume, ChartTuple[12]$quoteAssetVolume)
  amount <- c(amount, value)
  value <- value * 1.0001
}



# Build chartData Dataframe
chartData <- data.frame(amount, openTime, open, high, low, close, volume, closeTime, quoteVolume, trades, baseAssetVolume, quoteAssetVolume)
```


Add on additional parameters
```{r}

```


Plot Data to find Clusters
```{r}
plot(chartData)
```

Attempt Linear Regression Net Anaylsis
```{r}
chartlm <- lm(amount~., data=chartData)

summary(chartlm)

```


Attempt Simple Neural Net Anaylsis
```{r}
library(neuralnet)


```

Attempt PCA Anaylsis
```{r}

```

Attempt MultiModel Anaylsis
```{r}

```


`Using a classification variable try to setup a buy and sell frequence to factor in!!!!`
Attempt Classification Analysis
```{r}

```